Combine Files

### 2023-05-07 manuscript_scopus.Rmd
manuscript files

# maybe try binning
DF$geo_country$count_binned <- if_else(
  DF$geo_country$count >= 10000, "10,000+", 
  if_else(
    DF$geo_country$count < 10000 & DF$geo_country$count >= 5000, "5,000-9,999",
    if_else(
      DF$geo_country$count < 5000 & DF$geo_country$count >= 1000, "1,000-4,999",
      if_else(
        DF$geo_country$count < 1000 & DF$geo_country$count >= 100, "100-999",
        "< 100"
      )
    )
  )
)

@@

DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
                                      levels = c("< 100", 
                                                 "100-999", 
                                                 "1,000-4,999", 
                                                 "5,000-9,999", 
                                                 "10,000+"))

@@

@@

```{r geo-map-all}
# maybe try binning
DF$geo_country$count_binned_all <- if_else(
  DF$geo_country$count_all >= 10000, "10,000+", 
  if_else(
    DF$geo_country$count_all < 10000 & DF$geo_country$count_all >= 5000, "5,000-9,999",
    if_else(
      DF$geo_country$count_all < 5000 & DF$geo_country$count_all >= 1000, "1,000-4,999",
      if_else(
        DF$geo_country$count_all < 1000 & DF$geo_country$count_all >= 100, "100-999",
        "< 100"
      )
    )
  )
)

@@

DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
                                      levels = c("< 100", 
                                                 "100-999", 
                                                 "1,000-4,999", 
                                                 "5,000-9,999", 
                                                 "10,000+"))

>>>>

# maybe try binning
DF$geo_country$count_binned <- if_else(
  DF$geo_country$count >= 1000000, "1,000,000+", 
  if_else(
    DF$geo_country$count >= 500000 & DF$geo_country$count < 1000000, "500,000-999,999",
    if_else(
      DF$geo_country$count >= 100000 & DF$geo_country$count < 500000, "100,000-499,999",
      if_else(
        DF$geo_country$count >= 10000 & DF$geo_country$count < 100000, "10,000-99,999", 
        if_else(
          DF$geo_country$count < 10000 & DF$geo_country$count >= 5000, "5,000-9,999",
          if_else(
            DF$geo_country$count < 5000 & DF$geo_country$count >= 1000, "1,000-4,999",
            if_else(
              DF$geo_country$count < 1000 & DF$geo_country$count >= 100, "100-999",
              "< 100"
            )
          )
        )
      )
    )
  )
)

@@

DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
                                      levels = c("< 100", 
                                                 "100-999", 
                                                 "1,000-4,999", 
                                                 "5,000-9,999", 
                                                 "10,000-99,999",
                                                 "100,000-499,999",
                                                 "500,000-999,999",
                                                 "1,000,000+"))

@@

# Warning: Some values were not matched unambiguously: ANT, ATA, BUR, BUX, BYS, CAI, CSK, CZH, DDR, EUE, HVO, PCI, ROM, SUN, SUX, TWN, UNO, YMD, YUG, ZAR

@@

```{r geo-map-all}
# maybe try binning
DF$geo_country$count_binned_all <- if_else(
  DF$geo_country$count_all >= 1000000, "1,000,000+", 
  if_else(
    DF$geo_country$count_all >= 500000 & DF$geo_country$count_all < 1000000, "500,000-999,999",
    if_else(
      DF$geo_country$count_all >= 100000 & DF$geo_country$count_all < 500000, "100,000-499,999",
      if_else(
        DF$geo_country$count_all >= 10000 & DF$geo_country$count_all < 100000, "10,000-99,999", 
        if_else(
          DF$geo_country$count_all < 10000 & DF$geo_country$count_all >= 5000, "5,000-9,999",
          if_else(
            DF$geo_country$count_all < 5000 & DF$geo_country$count_all >= 1000, "1,000-4,999",
            if_else(
              DF$geo_country$count_all < 1000 & DF$geo_country$count_all >= 100, "100-999",
              "< 100"
            )
          )
        )
      )
    )
  )
)

@@

DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
                                      levels = c("< 100", 
                                                 "100-999", 
                                                 "1,000-4,999", 
                                                 "5,000-9,999", 
                                                 "10,000-99,999",
                                                 "100,000-499,999",
                                                 "500,000-999,999",
                                                 "1,000,000+"))
